---
title: "day_8_activities"
author: "Joe DeCesaro"
date: "8/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(patchwork)
library(ggrepel)
library(gghighlight)
library(paletteer)
library(ggExtra)
library(ggbeeswarm)
library(gapminder)
library(directlabels)

```

## Task 1: Do your data viz worst

```{r}
space_launches <- read_csv(here("data", "space_launches.csv"))

space_launches_year_count <- space_launches %>% 
  group_by(launch_year) %>% 
  summarize(launches_per_year = n())
```

```{r}
space_launches <- ggplot(space_launches_year_count, aes(x = launch_year, y = launches_per_year)) +
  geom_line(color = "pink", size = 15) + 
  geom_point(shape = 3) +
  labs(x = "Year",
       y = "Number of Launches",
       title = "SPACE") +
  theme(
    plot.background = element_rect(fill = "cyan"),
    panel.grid = element_line(color = "red4", 
                              size = 10), 
    axis.title.x = element_text(face = "bold.italic",
                                family = "NewCenturySchoolbook",
                                angle = 40),
    axis.title.y = element_text(face = "italic",
                                color = "orange",
                                angle = 180,
                                size = 20)) + 
  scale_color_gradientn(colors = c("red","orange","yellow"))


space_launches
```

## Task 2: Wrangling practice with the SF Greenhouse Gas data
```{r}
san_fran <- read_csv(here("data", "San_Francisco_Communitywide_Greenhouse_Gas_Inventory.csv"))

san_fran <- san_fran %>% 
  clean_names()
```
1. Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by sector_general
```{r}
tot_annual_sector <- san_fran %>% 
  group_by(sector_general, calendar_year) %>% 
  summarize(total_annual_ghg_emissions = sum(emissions_mt_co2e, na.rm = TRUE))
```

2. Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by year and commodity type
```{r}
tot_annual_comm <- san_fran %>% 
  group_by(commodity_type, calendar_year) %>% 
  summarize(total_annual_ghg_emissions = sum(emissions_mt_co2e, na.rm = TRUE))
```

3. Create a subset of the data that only contains observations from 2005 on, only for observations where Sector_Detail2 contains the pattern “PG&E”, then limit to columns Calendar_Year, Sector_Detail2 and Emissions_mtCO2e.
```{r}
san_fran_2005 <- san_fran %>% 
  filter(calendar_year >= 2005) %>% 
  filter(str_detect(sector_detail2, "PG&E")) %>% 
  select(calendar_year,sector_detail2,emissions_mt_co2e)
```

## Task 3: Do your data viz best
```{r}
tot_sector <- tot_annual_sector %>% 
  filter(calendar_year >= 2015)

ggplot(tot_sector, aes(x = calendar_year, y = total_annual_ghg_emissions, color = sector_general)) + 
  geom_line(aes(group = sector_general), 
            show.legend = FALSE) +
  geom_text(data = tot_sector %>% 
              filter(calendar_year == last(calendar_year)), aes(label = sector_general,
                                                                x = calendar_year + 0.4,
                                                                y = total_annual_ghg_emissions + 45000,
                                                                color = sector_general),
            show.legend = FALSE,) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "grey"),
    panel.background = element_blank(),
    axis.title.y = element_text(angle = 0)
  ) +
  xlim(2015, 2019.7) +
  labs(
    x = "Year",
    y= "Total Annual 
    GHG Emissions 
    (mtCO2e)",
    title = "Total Annual GHG Emissions in Megatons of CO2 Equivalents 
    from 2015 - 2019 by each Sector"
  ) 

 

```

